---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foofactorsmiller

<!-- badges: start -->
<!-- badges: end -->

The goal fo foofactorsmiller is to create a new factor from two existing factors, where the new factor's levels
are the union of the levels of the input factors.

## Installation

You can install the released version of foofactorsmiller from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("foofactorsmiller")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aromatic-toast/foofactorsmiller")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(foofactorsmiller)
## basic example code
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1,11,21)])
fcount(iris$Species)
```

